---
title: "STAT 530 Homework 3"
subtitle: "See schedule for due date"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions

Submit your answers on Compass in a PDF file created using an R notebook.

# Problem 1 (5 points)

Using the data in `tt2.RData` available on the Canvas site, find which gene is the most variable among myeloma patients treated with TT2. Provide your code in R chunks below each of the following steps.

1. Load the data. (1 point)

```{r}
## part 1 R code here
```

2. Find the probe ID with the highest standard deviation across the patients. (2 points)

```{r}
## part 2 R code here
```

3. Report the corresponding gene name. (1 point)

4. Visualize the results. Hint: look at previous homeworks in this class for relevant R functions. (1 point)

```{r}
## part 4 R code here
```

# Problem 2 (10 points, 1 per exercise)
Read [https://adv-r.hadley.nz/vectors-chap.html](https://adv-r.hadley.nz/vectors-chap.html) and complete the following exercises.

1. Section 3.2.5 Exercise 2

2. Section 3.2.5 Exercise 3

3. Section 3.3.4 Exercises 2

4. Section 3.3.4 Exercises 3

5. Section 3.4.5 Exercises 2

6. Section 3.4.5 Exercises 3

7. Section 3.5.4 Exercise 2

8. Section 3.6.8 Exercises 1

9. Section 3.6.8 Exercises 2

10. Section 3.6.8 Exercises 4